---
title: "rspm_demo"
author: "Jeremy Allen"
date: '2022-04-20'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Package Management in R

## Install your first package

```{r}

install.packages("pins")

```

Check the version of pins

```{r}

packageVersion("pins")

```

Load and use the pins package

```{r}

# load the package from the library
library(pins)

# pin some data to RStudio Connect so others can use it
board <- board_rsconnect(server = "colorado.rstudio.com")
pin_write(board = board, mtcars, name = "mtcars_dataframe")

```

Now that data frame lives on RStudio Connect so others can use the pins package to find it and use it without having to email CSV files around!

## Understanding your package environment

### Repositories

The big hardware store is the place where sets of tools are organized and distributed. Your repos might be different than mine! See Tools -\> Global Options to chose another repo.

```{r}

getOption("repos")

```

### Libraries

The workshop of tools in your garage contains the sets of tools you bought from the big hardware store.

-   R libraries are tied to R versions

-   Three types of libraries: System, User, Project

```{r}

.libPaths()

```

# RStudio Package Manager Demo

## Install Package

```{r}

install.packages("ggplot2")
packageVersion("ggplot2")

```

## Where did it come from?

```{r}

getOption("repos")

```

## How fast are binaries?

```{r}

# install compile from source

options(repos = c(REPO_NAME = "https://colorado.rstudio.com/rspm/cran/latest"))

system.time(
utils::install.packages("dplyr", repos = "https://colorado.rstudio.com/rspm/cran/latest")
)

```

```{r}

# install binary

options(repos = c(REPO_NAME = "https://colorado.rstudio.com/rspm/cran/__linux__/focal/latest"))

system.time(
utils::install.packages("dplyr", repos = "https://colorado.rstudio.com/rspm/cran/__linux__/focal/latest")
)

```

## Time Travel

Install dplyr as if back in March 2021

```{r}

# set repo
options(repos = c(REPO_NAME = "https://colorado.rstudio.com/rspm/cran/__linux__/focal/2021-03-31"))

#install
utils::install.packages("dplyr")

packageVersion("dplyr")
```

Install dplyr as of March 2022

```{r}

# set repo
options(repos = c(REPO_NAME = "https://colorado.rstudio.com/rspm/cran/__linux__/focal/2022-03-31"))

#install
utils::install.packages("dplyr")

packageVersion("dplyr")

```

## Install from a curated and frozen repo

```{r}

# set repo
options(repos = c(REPO_NAME = "https://colorado.rstudio.com/rspm/curated/__linux__/focal/2020-05-30+ODozNTY4O0M5RkRBMTgz"))

#install
utils::install.packages("dplyr")

packageVersion("dplyr")


```

## Install with renv

restart R session first

```{r}

#install
install.packages("dplyr")

packageVersion("dplyr")

```

## Install from Bioconductor

```{r}

# install BiocManager
install.packages("BiocManager")

# install Biobase
BiocManager::install("Biobase", force = TRUE)


```
